### 2019-11-21 manuscript/manuscript.rmd
pass at au test / phylogenetic signal plot

phylogenetic_signal_by_genes <- rbind(Philippe2009_count, Philippe2009_WAG_count, Philippe2009_only_choanozoa_count, Philippe2009_WAG_only_choanozoa_count,  Ryan2013_count, Ryan2013_WAG_count, Ryan2013_only_choanozoa_count, Ryan2013_WAG_only_choanozoa_count, Whelan2017_full_count, Whelan2017_full_WAG_count,  Whelan2017_full_only_choanozoa_count, Whelan2017_full_WAG_only_choanozoa_count)
ggplot(phylogenetic_signal_by_genes, aes(x = study, y = perc, fill=result)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle=45)) +  scale_fill_manual(values=c("#E69F00", "#999999","#009E73", "#999999" ))

>>>>

```{r phylogenetic_signal}
au_tests %>%
  unite(Matrix, c(manuscript, matrix)) %>%
  group_by(Matrix, result) %>%
  count() %>%
  group_by(Matrix) %>%
  mutate(percent = prop.table(n)) %>%

ggplot(aes(x = Matrix, y = percent, fill=result)) + 
  geom_bar(stat = "identity") +
  #scale_y_continuous(limits = c(0,1), expand = c(0, 0))+
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  scale_fill_manual(values=c("#E69F00", "#ebd196","#a2e8d5","#009E73"))
